---
title: "workout01-Lingfei-Wu"
author: "Lingfei Wu"
date: "October 2, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.path = '../report/workout01-Lingfei-Wu_files/')
```

```{r}
dat <- read.csv('../data//nba2018-teams.csv')
library('ggplot2')
```



```{r NBA Teams Ranked by Total Salary}
ggplot(dat, aes(x=reorder(team,salary),y=salary)) +
  geom_bar(stat='identity') +
  coord_flip()+ 
  geom_hline(yintercept=mean(dat$salary),color="red",size=2)+
  xlab("Team") + ylab("Salary(in millions)")+labs(title="NBA Teams Ranked by Total Salary")

```


```{r NBA Teams Ranked by Total Points}
ggplot(dat, aes(x=reorder(team,points),y=points)) +
  geom_bar(stat='identity') +
  coord_flip()+ 
  geom_hline(yintercept=mean(dat$points),color="red",size=2)+
  xlab("Team") + ylab("Points")+labs(title="NBA Teams Ranked by Total Points")

```


```{r NBA Teams Ranked by Total Efficiency}
ggplot(dat, aes(x=reorder(team,efficiency),y=efficiency)) +
  geom_bar(stat='identity') +
  coord_flip()+ 
  geom_hline(yintercept=mean(dat$efficiency),color="red",size=2)+
  xlab("Team") + ylab("Efficiency")+labs(title="NBA Teams Ranked by Total Efficiency")

```


```{r}
myefficiency <-  1-4*(dat$turnovers+dat$fouls)/(dat$points+dat$off_rebounds
             +dat$def_rebounds+dat$assists+dat$steals+dat$blocks+dat$turnovers)
``` 

I first compute the ratio of negative behaviors to positive behaviors, and enlarge this error rate by 4 times. Since the team who has the larger error rate performs worse, I use 1 to subtract it and get my efficiency.


```{r NBA Teams Ranked by My Efficiency}
ggplot(dat, aes(x=reorder(team,myefficiency),y=myefficiency)) +
  geom_bar(stat='identity') +
  coord_flip()+ 
  geom_hline(yintercept=mean(myefficiency),color="red",size=2)+
  xlab("Team") + ylab("My Efficiency")+labs(title="NBA Teams Ranked by My Efficiency")

```



### Comments and Reflections
* Yes.I think we should be more cautious about the path.
* No.
* No.
* Using ggplot and push the commits to my github repository.
* Writing the data dictionary.
* No.
* 7 hours.
* Ranking the teams.
* Working with the file structure.

